A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-09 doc/draft-01-stokes/04numerical.tex
minor updates

The \texttt{roots} utility returns the roots
of the polynomial in the complex plane, with
some minimal internal processing to remove
spurious roots.
%
Because our numerical determinant evaluation
is somewhat noisy and we fit the function up to
precision $\epscheb$, we perform some
further post-processing to eliminate remaining
spurious roots.
%
Let $\kcheb_l$ denote the roots of the interpolants.
%
We ignore any of the returned roots with $|\imag(\kcheb_l)|
> \sqrt{\epscheb}$, as these are too far from real-valued
to be non-spurious.
%
For the remaining roots, we consider the
properties of $\real(\kcheb_l)$.
%
We inspect any pairs of roots $(\kcheb_p,\kcheb_q)$
for which $|\real(\kcheb_p-\kcheb_q)| < \sqrt{\epscheb}$,
as these are possibly spurious double roots.
%
For these pairs, we compare the right singular
vector of the appropriate BIE operator corresponding
to the smallest singular value for each of $k=\real(\kcheb_p)$
and $k=\real(\kcheb_p)$, which we denote by
$\bv_p$ and $\bv_q$.
%
If $\|\bv_p - \bv_q \bv_q^* \bv_p \| < 10^{-5}$, then
we consider the pair to be spurious.
%
For these near double-roots, we also check
that there is no two dimensional null-space
corresponding to the root by estimating the
second smallest singular value of the BIE operator.
%
If this is larger than $10^{-5}$, then we declare
it to be a simple root.

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 135 total roots: 3 were removed because
the imaginary part was too large and 13 pairs were found
with values within $\epsclose = 10^{-5}$ of each other.
%
For these 13 pairs, none represented two distinct
eigenvalues or a double root and all were in fact
much closer than $\epsclose$.
%
This leaves 119 roots in the range $0\leq k \leq 6.5$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2\cW^N$ for each of these roots in
\cref{subfig:barbell_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:barbell_gallery}.
%
The singular values suggest that the quality of the
eigenvalues is good.
From the plots, we see that localization occurs
until about the 100th eigenvalue.

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\epsclose = 10^{-5}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root and all were in fact
much closer than $\epsclose$.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^n-2\cW^N$ for each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
The singular values suggest that the quality of the
eigenvalues is good, with a few outliers.
%
These outliers correspond to eigenvalues 9 through 12,
which have 
The conditioning of the eigenvalue problem depends
on the distance to the nearest eigenvalue. For
the 8th through 13th eigenvalues, the average
spacing between consecutive roots is 0.0447,
which is much smaller than the average spacing of
the roots for the first 20 eigenvalues, given by
0.1132.
In the plots, we observe a different type of
localization property, with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\note{cite}

>>>>

The \texttt{roots} utility returns the roots
of the polynomial in the complex plane, with
some minimal internal processing to remove
spurious roots.
%
Because our numerical determinant evaluation
is somewhat noisy and we fit the function up to
precision $\epscheb$, we perform some
further post-processing to eliminate remaining
spurious roots.
%
Let $k^{(l)}_\cheb$ denote the roots of the interpolants.
%
We ignore any of the returned roots with $|\imag(k^{(l)}_\cheb)|
> \sqrt{\epscheb}$, as these are too far from real-valued
to be non-spurious.
%
For the remaining roots, we consider the
properties of $\real(k^{(l)}_\cheb)$.
%
We inspect any pairs of roots $(k^{(p)}_\cheb,k^{(q)}_\cheb)$
for which $|\real(k^{(p)}_\cheb-k^{(q)}_\cheb)| < \sqrt{\epscheb}$,
as these are possibly spurious double roots.
%
For these pairs, we compare the right singular
vector of the appropriate BIE operator corresponding
to the smallest singular value for each of $k=\real(k^{(p)}_\cheb)$
and $k=\real(k^{(p)}_\cheb)$, which we denote by
$\bv_p$ and $\bv_q$.
%
If $\|\bv_p - \bv_q \bv_q^* \bv_p \| < 10^{-5}$, then
we consider the pair to be spurious.
%
For these near double-roots, we also check
that there is no two dimensional null-space
corresponding to the root by estimating the
second smallest singular value of the BIE operator.
%
If this is larger than $10^{-5}$, then we declare
it to be a simple root.

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 135 total roots: 3 were removed because
the imaginary part was too large and 13 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 13 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 119 roots in the range $0\leq k \leq 6.5$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2\cW^N$ for each of these roots in
\cref{subfig:barbell_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:barbell_gallery}.
%
The singular values suggest that the quality of the
eigenvalues is good.
From the plots, we see that localization occurs
until about the 100th eigenvalue.

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
The singular values suggest that the quality of the
eigenvalues is good, with a few outliers.
%
These outliers correspond to eigenvalues 9 through 12,
which have 
The conditioning of the eigenvalue problem depends
on the distance to the nearest eigenvalue. For
the 8th through 13th eigenvalues, the average
spacing between consecutive roots is 0.0447,
which is much smaller than the average spacing of
the roots for the first 20 eigenvalues, given by
0.1132.
In the plots, we observe a different type of
localization property, with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\note{cite}
